MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-02 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='add-dream')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21754352'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL

@@

#Get Metadata
metadata = 'syn16816488' 
ALL_USED_IDs[length(ALL_USED_IDs)+1] = metadata
metadata = downloadFile_version(metadata, version = 16)  %>% 
  dplyr::select(Individual_ID, Institution, Reported_Gender, Sex, 
                Ethnicity, ageOfDeath, `PMI_(in_hours)`, Dx,
                Sample_RNA_ID, one_of('rnaSeq_isolation:RIN',
                                      'rnaSeq_report:Ribozero_Batch', 'rnaSeq_report:Library_Batch', 
                                      'rnaSeq_report:Flowcell_Batch','rnaSeq_dissection:Brain_Region',
                                      'rnaSeq_report:Exclude?',
                                      'rnaSeq_report:Mapped_Reads',
                                      'rnaSeq_report:Intragenic_Rate','rnaSeq_report:Intronic_Rate',
                                      'rnaSeq_report:Intergenic_Rate','rnaSeq_report:Genes_Detected',
                                      'rnaSeq_report:Expression_Profiling_Efficiency',
                                      'rnaSeq_report:rRNA_Rate',
                                      'rnaSeq_report:Total_Reads', 'rnaSeq_report:Percent_Aligned'))

>>>>

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='add-dream')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21867938'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL

@@

#Get Metadata
metadata = 'syn16816488' 
ALL_USED_IDs[length(ALL_USED_IDs)+1] = metadata
metadata = downloadFile_version(metadata, version = 17)  %>% 
  dplyr::select(Individual_ID, Institution, Reported_Gender, Sex, 
                Ethnicity, ageOfDeath, `PMI_(in_hours)`, Dx,
                Sample_RNA_ID, one_of('rnaSeq_isolation:RIN',
                                      'rnaSeq_report:Ribozero_Batch', 'rnaSeq_report:Library_Batch', 
                                      'rnaSeq_report:Flowcell_Batch','rnaSeq_dissection:Brain_Region',
                                      'rnaSeq_report:Exclude?',
                                      'rnaSeq_report:Mapped_Reads',
                                      'rnaSeq_report:Intragenic_Rate','rnaSeq_report:Intronic_Rate',
                                      'rnaSeq_report:Intergenic_Rate','rnaSeq_report:Genes_Detected',
                                      'rnaSeq_report:Expression_Profiling_Efficiency',
                                      'rnaSeq_report:rRNA_Rate',
                                      'rnaSeq_report:Total_Reads', 'rnaSeq_report:Percent_Aligned'))
